---
title: "Graphs"
author: "Djebari"
date: '2022-06-27'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Libraries

```{r}
library(tidyverse)
library(recommenderlab)
library(lubridate)
library(scales)
```


#rating frequency
```{r}
data_rating_frequency %>% 
  count(rating) %>% 
  mutate(rating = as.factor(rating)) %>% 
  ggplot(aes(y = n, x = "",fill = rating))+
  geom_bar(width = 1, stat = "identity")+
  coord_polar("y", start = 0) +
  geom_text(aes(label = paste0(round(n/sum(n),2)*100, "%")),
            position = position_stack(vjust = 0.5))+
  labs(x="", y= "", fill= "note")+
  theme_minimal()+
  theme(axis.text.x = element_blank())
```

#average rating of each item
```{r}
data_rating_frequency %>% 
  group_by(food_name2) %>%
  mutate(avg_rating = mean(rating)) %>%
  ungroup() %>%
  ggplot(aes(avg_rating)) +
  geom_histogram(fill = "firebrick") +
  scale_y_continuous(labels = number_format(big.mark = ",")) +
  labs(x = "Note moyenne", y = "Fréquence absolue") +
  theme_classic()+
  theme(axis.text.y = element_blank())
```

#average rating of each item (items <= 3.5)
```{r}
data_rating_frequency %>% 
  group_by(food_name2) %>%
  mutate(avg_rating = mean(rating)) %>%
  ungroup() %>%
  filter(avg_rating <= 3.5) %>%
  ggplot(aes(avg_rating)) +
  geom_histogram(fill = "firebrick") +
  scale_y_continuous(labels = number_format(big.mark = ",")) +
  labs(x = "Note moyenne", y = "Fréquence absolue") +
  theme_classic()+
  theme(axis.text.y = element_blank())
```

#average rating of each item (items > 3.5)
```{r}
data_rating_frequency %>% 
  group_by(food_name2) %>%
  mutate(avg_rating = mean(rating)) %>%
  ungroup() %>%
  filter(avg_rating >3.5) %>%
  ggplot(aes(avg_rating)) +
  geom_histogram(fill = "firebrick") +
  scale_y_continuous(labels = number_format(big.mark = ",")) +
  labs(x = "Note moyenne ", y = "Féquence absolue") +
  theme_classic()+
  theme(axis.text.y = element_blank())
```

#average rating for each user
```{r}
data_rating_frequency %>% 
  group_by(user_id) %>%
  mutate(avg_rating = mean(rating)) %>%
  ungroup() %>%
  ggplot(aes(avg_rating)) +
  geom_histogram(fill = "firebrick") +
  scale_y_continuous(labels = number_format(big.mark = ",")) +
  labs(x = "Note moyenne", y = "Fréquence absolue") +
  theme_classic()+
  theme(axis.text.y = element_blank())
```

#ratings of 5 best users for all their items
```{r}
a <- data_rating_frequency %>%
  count(user_id) %>%
  arrange(-n) %>%
  slice(1:5) %>%
  pull(user_id)


data_rating_frequency %>%
  filter(user_id %in% a) %>%
  # group_by(user_id, food_name2) %>%
  # mutate(n = n()) %>%
  # ungroup() %>%
  # arrange(-n) %>%
  # slice(1:10) %>%
  ggplot(aes(x = food_name2, y = user_id, fill = factor(rating))) +
  geom_tile() +
   labs(x="Plats", y="Identifiant de l'utilisateur", fill = "Notes")+
  scale_fill_discrete() +
  theme_classic()+
  theme(#axis.ticks.x = element_blank(),
        axis.text.x = element_blank())
```

#purchase frequency by days and hours
```{r}
data %>%
  mutate(jour_de_semaine = weekdays(as.POSIXct(request_date)), 
         heure = hour(as.POSIXct(request_date))) %>% 
  count(jour_de_semaine, heure) %>% 
  ggplot(aes(x = heure, y = ordered(jour_de_semaine, c("dimanche", "lundi", "mardi","mercredi", "jeudi", "vendredi", "samedi")), fill = n)) +
  labs(y="jour")+
  geom_tile() +
  scale_fill_viridis_c() +
  scale_x_continuous(breaks = 0:23) + 
  theme_classic()
```

